Effects of the body force on the evacuation dynamics

### 2020-02-03 paper.tex
corregi la cita que sita el parametro experimental que es 2.62E4

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./vd_vs_te_N225.eps}
\caption{\label{vd_vs_te}Mean evacuation time (s) vs. the pedestrian’s desired  
velocity (m/s) for a bottleneck. The room was 20 m x 20 m size. The door was 
0.92 m width. Mean values were computed from 10 evacuation processes. 225 
pedestrians were initially placed in a square lattice with a random initial 
velocity. Each process was finished when 158 pedestrians left the room. The 
different symbols indicate the $k_n$ value corresponding to the body force (see 
the label). The crosses correspond to the Helbing's original SFM parameter, the 
up-triangles correspond to the value measured in 
Ref.~\cite{anthropometric}, squares correspond 
to zero body force and circles correspond to an extreme value of stiffness (one 
order of magnitude higher than the original SFM). The 
 down triangles correspond to an intermediate value between the empirical value 
presented in Ref.~\cite{anthropometric} and the chosen by Helbing in 
Ref.~\cite{helbing_2000} }
\end{figure}

>>>>

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./vd_vs_te_N225.eps}
\caption{\label{vd_vs_te}Mean evacuation time (s) vs. the pedestrian’s desired  
velocity (m/s) for a bottleneck. The room was 20 m x 20 m size. The door was 
0.92 m width. Mean values were computed from 10 evacuation processes. 225 
pedestrians were initially placed in a square lattice with a random initial 
velocity. Each process was finished when 158 pedestrians left the room. The 
different symbols indicate the $k_n$ value corresponding to the body force (see 
the label). The crosses correspond to the Helbing's original SFM parameter, the 
up-triangles correspond to the value measured in 
Ref.~\cite{melvin1988aatd}, squares correspond 
to zero body force and circles correspond to an extreme value of stiffness (one 
order of magnitude higher than the original SFM). The 
 down triangles correspond to an intermediate value between the empirical value 
presented in Ref.~\cite{melvin1988aatd} and the chosen by Helbing in 
Ref.~\cite{helbing_2000} }
\end{figure}
